Calculating Entropies With Nested Sampling

### 2017-03-05 paper/ms.tex
Moved a figure

\subsection{Results}
Letting $\tau = \log_{10} T$, and treating
$A$ and $\phi$ are nuisance parameters, I calculated the entropies
of $\tau$, $\d$, and $(\tau, \d)$.
These results were computed using a tolerance of 0.001 for each of the three
runs. The results are:
\begin{align}
H_{\tau}    &= 7.307 \pm 0.027 \\
H_{\d}      &= 900.6 \pm 1.1   \\
H_{\tau,\d} &= 882.2 \pm 1.1
\end{align}

@@

The computational resources needed to compute these quantities was quite large
--- three lots of 1,000 repetitions of Nested Sampling, in all
(though the algorithm can be parallelised trivially).
However, it is worth reflecting on the difficulty of the calculation that
has been done.

>>>>

\subsection{Results}

Letting $\tau = \log_{10} T$, and treating
$A$ and $\phi$ are nuisance parameters, I calculated the entropies
of $\tau$, $\d$, and $(\tau, \d)$.
These results were computed using a tolerance of 0.001 for each of the three
runs. The results are:
\begin{align}
H_{\tau}    &= 7.307 \pm 0.027 \\
H_{\d}      &= 900.6 \pm 1.1   \\
H_{\tau,\d} &= 882.2 \pm 1.1
\end{align}

@@

The computational resources needed to compute these quantities was quite large
--- three lots of 1,000 repetitions of Nested Sampling, in all
(though the algorithm can be parallelised trivially).
However, it is worth reflecting on the complexity of the calculation that
has been done.
